Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-10-20 paper/paper.Rmd
adds new comments

Overall, `r round(length(id_na) / nrow(answers) * 100, 1)`% of the participants reported that currently no packages and functionality are missing for them or they lack the overview to answer the question.
There were two most common topics across the answers of the participants . 
Firstly, many participants (`r perc_performance`%) wished for a better computational performance of *R* in terms of speed and required RAM for larger data.
Secondly, many participants (`r perc_viz`%) are currently missing advanced and easy-to-apply methods for creating high-quality maps or other visualization-related functionality.
Fewer participants were missing tools for various connectivity-related issues (`r perc_viz`%) and characterization of landscape characteristics (`r perc_characterisation`%).

@@

>>>>

Overall, `r round(length(id_na) / nrow(answers) * 100, 1)`% of the participants reported that currently no packages and functionality are missing for them or they lack the overview to answer the question.
There were two most common topics across the answers of the participants. 
Firstly, many participants (`r perc_performance`%) wished for a better computational performance of *R* in terms of speed and required RAM for larger data.
Secondly, many participants (`r perc_viz`%) are currently missing advanced and easy-to-apply methods for creating high-quality maps or other visualization-related functionality.
Fewer participants were missing tools for various connectivity-related issues (`r perc_viz`%) and characterization of landscape characteristics (`r perc_characterisation`%).

@@

<!--JN: I think we should answer to some of the comments in the missing packages section: point people to some packages (if possible), mention which of the missing tools are not going to be implemented, and also forward people to methods and tools on how to improve some problems (e.g. speed and required RAM for larger data -> use of Rcpp, use external servers, or read data in chunks, etc.)-->

### 2020-10-20 paper/paper.tex
adds new comments

@@

The survey also included a section in which participants could list methods and tools that are currently missing in \emph{R} and answers to this question were very diverse.
Overall, 21.9\% of the participants reported that currently no packages and functionality are missing for them or they lack the overview to answer the question.
There were two most common topics across the answers of the participants .
Firstly, many participants (13.5\%) wished for a better computational performance of \emph{R} in terms of speed and required RAM for larger data.
Secondly, many participants (9.4\%) are currently missing advanced and easy-to-apply methods for creating high-quality maps or other visualization-related functionality.
Fewer participants were missing tools for various connectivity-related issues (9.4\%) and characterization of landscape characteristics (7.3\%).

>>>>

Most of landscape metrics are a single number depicting specific characteristics of a local landscape.
Another possibility is to derive spatial signatures - a multi-value representation of landscape composition and configuration, such as a co-occurrence histogram.
Spatial signatures calculated for many landscapes can be compared using one of the existing distance measures.
This enables several types of spatial analysis on categorical raster data, such as searching for similar landscapes, detecting changes between landscape patterns, and spatial clustering of landscapes based on their composition and configuration.
Methods for pattern-based spatial analysis are implemented in the \emph{motif} package \cite{R-motif}.

@@

The survey also included a section in which participants could list methods and tools that are currently missing in \emph{R} and answers to this question were very diverse.

Overall, 21.9\% of the participants reported that currently no packages and functionality are missing for them or they lack the overview to answer the question.
There were two most common topics across the answers of the participants .
Firstly, many participants (13.5\%) wished for a better computational performance of \emph{R} in terms of speed and required RAM for larger data.
Secondly, many participants (9.4\%) are currently missing advanced and easy-to-apply methods for creating high-quality maps or other visualization-related functionality.
Fewer participants were missing tools for various connectivity-related issues (9.4\%) and characterization of landscape characteristics (7.3\%).
